%\documentclass[12pt]{article}
\documentclass[12pt, oneside, letterpaper]{book}
\title{CHEM 121: Nomenclature practice}
\nonstopmode
\usepackage{graphicx} % Required for including pictures
\usepackage[figurename=Figure]{caption}
\usepackage{float}    % For tables and other floats
\usepackage{verbatim} % For comments and other
\usepackage{amsmath}  % For math
\usepackage{amssymb}  % For more math
\usepackage{fullpage} % Set margins and place page numbers at bottom center
\usepackage{paralist} % paragraph spacing
\usepackage{listings} % For source code
\usepackage{subfig}   % For subfigures
%\usepackage{physics}  % for simplified dv, and 
\usepackage{wrapfig}
\usepackage{enumitem} % useful for itemization
\usepackage{siunitx}  % standardization of si units

\usepackage{tikz,bm} % Useful for drawing plots
%\usepackage{tikz-3dplot}
\usepackage{circuitikz}
\usepackage{url}
\usepackage[table]{xcolor}
%Settings parameters for how tables will be formatted
\setlength{\arrayrulewidth}{0.5mm}
\setlength{\tabcolsep}{20pt}
%Package to help with formatting chemical formulae
\usepackage[version=4]{mhchem}

\usepackage{fontspec}
\usepackage{gensymb}
\usepackage{titlesec}


\usepackage{fancyhdr}

\usepackage[paperheight=280mm, paperwidth=216mm,
nomarginpar,% We don't want any margin paragraphs
textwidth=175mm,% Set \textwidth to 10cm
headheight=8mm]% Set \headheight to 10mm%]% Set \headheight to 10mm
{geometry}

\titleformat{\section}
  {\center\normalfont\normalsize\bfseries}{}{2em}{}
\titleformat{\subsection}
{\normalfont\normalsize\bfseries}{}{1em}{}
\titleformat{\paragraph}
{\normalfont\normalsize\mdseries}{}{0em}{}

\usepackage[skip=12pt plus1pt, indent=0pt]{parskip}
\usepackage{xfrac,unicode-math}
\setlist[itemize]{noitemsep}

\begin{document}

% Set the page style to "fancy"...
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhead{}
\fancyhead[R]{\thepage}
\fancyfoot{} % clear all footer fields
\renewcommand{\footrulewidth}{0.1pt}
\fancyfoot[L]{Truman Science Center}
\fancyfoot[C]{Calorimetry/Heat Capacity}
\fancyfoot[R]{15 April 2026}


\setmainfont{Arial}[Scale=0.9]
\setmathfont{Stix Two Math}[version=stix2]

\captionsetup{belowskip=1pt}


\begin{flushleft}
	\vspace{.3cm}
	{\textbf { \Large Calorimetry/Heat Capacity}}
\end{flushleft}
\vspace{1mm}
	\hrule

The equation below should come to mind whenever you see the question mention calorimetry, heat, or specific heat. 
\begin{gather*}
    Q=mc\ \Delta T
\end{gather*}

\section{{\normalsize The Process}}

\begin{enumerate}
   \item Assign any values given in the question to variables in the heat equation.
   \item Check the Units!!
   \begin{enumerate}
     \item Make sure the values you have for heat, mass, and temperature are the same as the units given in the specific heat. 
     \item Make sure your final answer is in the same units as the question asked for.
    \end{enumerate}
  \item Rearrange the heat equation so the variable you want to learn is isolated. 
  \item Plug in values 
\end{enumerate}

\section{\normalsize{Helpful Reference Values}}

\section{\normalsize{Values for Water}}
\begin{align*}
    &   c_{water}\ = 4.184\ \cfrac{J}{g\ \degree C} & d_{water}\ = 1\ \cfrac{g}{mL} &
\end{align*}

\section{\normalsize {Unit Conversions}}
\begin{align*}
    & 1\ Cal = 1000\ calories & 1\ calorie = 4.184\ J && \degree C\ - (\ \degree F - 32\ )\  \cdot \cfrac{5}{9} & 
\end{align*}

\newpage


\section{{\normalsize Calorimetry Practice}} 

\flushleft\flushleft{\normalsize{1) A $97.00\  g$ glass of water at $12.00\  \degree C$ is left on the countertop. The next day the temperature of the water is $23.00\  \degree C$, how much heat (in Joules) was absorbed by the water?}}
\vspace{4.5cm}

\flushleft{\normalsize{2) You have a special microwave button that releases $7.78\ kJ$ of heat into your food. You feel like playing Hot Potato so you put a $25\  \degree C$ potato into the microwave and turn it on. When it comes out it is $67\  \degree C$ and it burns your hand. If the specific heat capacity of potatoes is $3.43\  \cfrac{J}{g \degree C}$, what is the mass of the potato?}}
\vspace{4.5cm}

\flushleft{\normalsize{3) You left a $3.11\  g$ pure copper penny in your car which the sun heated to $32.00\  \degree C$. When you took the penny out it released $10.78 J$ of heat and its temperature went down to $23.00\ \degree C$. What is the specific heat capacity of Copper?}}

\newpage

\flushleft{\normalsize{4) You pick up a $0.24\ kg$ rock from a cold, $50\  \degree F$ natural spring. As it sits in the sun it heats up to $73.4\ \degree F$. It's specific heat capacity is $910\  \frac{mJ}{g \degree C}$, how much heat (in $kJ$) did the rock absorb?}}

\vspace{5cm}

\flushleft{\normalsize{5) You heat up a cast iron skillet that has a mass of $2.23\  kg$ to a temperature of $218\  \degree C$. How many $kJ$ are released from the skillet when it cools to room temperature $(22\  \degree C)$? The specific heat capacity of cast iron is $0.461\  \cfrac{J}{g \degree C}$}}
\vspace{5cm}

\flushleft{\normalsize{6) It takes $874.6\  kJ$ to heat up $3.12\  kg$ of water to its boiling point at $100\  \degree C$. What was the initial temperature of the water?}}
\newpage

\flushleft{\normalsize{7) A metal object releases $67.78\  kJ$ of energy into $300\  mL$ of water at $23\ \degree C$. What temperature does the water rise to assuming the density of water is $1.00\  \cfrac{g}{mL}$}}
\vspace{5cm}

\flushleft{\normalsize{8) When you set a Dorito on fire over a can of $50.0\ g$ of water, it releases $12.72\ Cal$ of energy. Assuming all of the energy goes into the water (and none into the can) what is the rise in temperature of the water?}}

\end{document}